Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
New return value table

\subsubsection{Relation}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
Return & 0.20 & 421 \\
Void & 0.19 & 2052 \\
Declare & 0.03 & 1318 \\
\rowcolor[HTML]{FFCCC9}
Assign & -1.29 & 3 \\ \bottomrule
\end{tabular}
\caption{Maintainability scores for different return values}
\label{tab:return}
\end{table}

>>>>

\subsubsection{Relation}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).

@@

\begin{table*}
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
%}
\caption{Average metric values for refactorings of clone classes with the specified return category}
\label{tab:return}
\end{table*}

The displayed return categories are ordered by their scores. Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability. When the result of the call to the extracted method is directly returns, the maintainability score is the highest. When no value is returned, the maintainability score is the lowest. The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
